Measurement and Probability in Fuzzy Quantum Theories

### 2017-06-16 prop_iop.tex
prop_iop.tex \subsection{From Real-valued to Interval-valued I} Updating

Although a convex interval-valued function\nb$\iota$ may look exotic,
its left end, defined by $\iotal\left(x\right)=\min\iota\left(x\right)$,
is well-studied Wright-convex satisfying $\iotal\left(x_{0}+x_{1}+x_{2}\right)+\iotal\left(x_{2}\right)\ge\iotal\left(x_{0}+x_{2}\right)+\iotal\left(x_{1}+x_{2}\right)$\nb\cite{Wright1954,RobertsVarberg1973,PecaricTong1992}.
After we define interval-valued function, we are ready to construct
a QIVPM from a quantum probability measure.

>>>>

Although a interval-valued function\nb$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
may look exotic, its left-end and right-end\nb$\left[\iotal\left(x\right),\iotar\left(x\right)\right]=\iota\left(x\right)$
are just usual functions from a unit interval to another unit interval.
For an additive interval-valued function, $\iotal$ is superadditive,
i.e., $\iotal\left(x_{0}+x_{1}\right)\ge\iotal\left(x_{0}\right)+\iotal\left(x_{1}\right)$,
and $\iotar$ is subadditive, i.e., $\iotar\left(x_{0}+x_{1}\right)\le\iotar\left(x_{0}\right)+\iotar\left(x_{1}\right)$\nb\cite{PecaricTong1992}.
For a convex interval-valued function, $\iotal$ is Wright-convex,
i.e., $\iotal\left(x_{0}+x_{1}+x_{2}\right)+\iotal\left(x_{2}\right)\ge\iotal\left(x_{0}+x_{2}\right)+\iotal\left(x_{1}+x_{2}\right)$,
and $\iotar$ is Wright-concave, i.e., $\iotar\left(x_{0}+x_{1}+x_{2}\right)+\iotar\left(x_{2}\right)\le\iotar\left(x_{0}+x_{2}\right)+\iotar\left(x_{1}+x_{2}\right)$\nb\cite{Wright1954,RobertsVarberg1973,PecaricTong1992,Brzdek_2014}.
Also, if $\mathscr{I}$ contains only finite number of intervals,
$\iotal$ and $\iotar$ must be step functions. After we define interval-valued
function, we are ready to construct a QIVPM from a quantum probability
measure.
